GEEPERs: Principal Stratification using Principal Scores and Stacked Estimating Equations

### 2022-12-05 writeUps/paper.tex
Updates from Overleaf

@@

In a separate, if related, line of research, \citet{jo2002}, \citet{ding2011}, \citet{jiangDing2021}, and others have shown that, under certain circumstances, researchers can use baseline covariates to identify and estimate principal effects without relying on principal ignorability.
This paper expands on those identification results by presenting a new set of principal effect estimators, and associated standard error estimates, based on a generalized estimating equations (or M-estimation or method-of-moments) \citep{stefanskiBoos}.
It turns out that, under certain general conditions, principal effects can be estimated with a simple, two-step procedure: first, estimate principal scores with logistic regression or another M-estimator; then, impute unknown principal subroup membership indicators with principal scores and estimate principal effects using OLS with interactions, just as in the pre-treatment subgroup case.
We will refer to the estimators presented here as ``GEEPERs'': generalized estimating equations for principal effects using regressions.
GEEPERs estimates rely on correct specification of regression functions, but unlike common fully-parametric methods, they make no assumptions about the distribution of regression errors.
Unlike principal score weighting, GEEPERs does not assume principal ignorability, and admits to sandwich-style standard error estimates, which we provide in the appendix.

@@

\subsubsection{Manipulated Factors}
We manipulated six factors in the simulation:

\begin{table}
  \centering
  \begin{tabular}{cc}
    \hline
    Factor &Levels\\
    \hline
Sample size per treatment group $n$ &$100,200,\dots,1000$\\
$\alpha$ &$0,0.2,0.3,\dots,1$\\
The distribution of $\epsilon_i$& Normal, Uniform\\
$\beta_1$ & 0, 0.3\\
Interactions between $\st$ and covariates & No, Yes\\
Interactions between $Z$ and covariates& No, Yes\\
\hline
  \end{tabular}
  \caption{Manipulated factors in simulation study}
  \label{tab:factor}
  \end{table}
The six factors are not completely crossed---in particular, we let $n$ and $\alpha$ each vary across all the levels listed while holding the other five factors fixed.

The guarentees of M-estimation are all asymptotic, so we examined the behavior of our M-estimator at a range of sample sizes to determine its finite-sample properties.

As mentioned above, $\alpha$ controls the variance of the principal scores, i.e. the extent to which $\st$ is predictable as a function of covariates. When $\alpha=0$, the covariates are unrelated to $\st$ and principal scores do not vary between participants, violating \eqref{ass:vps}. We expect that the more predictive the covariates, the better the performance of all three estimators.
To aid in the interpretation of the $\alpha$ parameter, the online appendix plots $\alpha$ against the area under the receiver operating characteristic curve for each fitted model (AUC), a common measure of classification accuracy \citep{bradley1997use}---an AUC of 0.5 implies that the model is no better than random guessing, and AUC of 1 implies perfect prediction. For $0.5\le \alpha \le 1$, the average AUC varies from roughly 0.53 to 0.77; for $\alpha=0.5$, the average AUC was roughly 0.675.

$\epsilon$ is the regression error in \eqref{eq:y-sim}. Across simulation runs, $E[\epsilon]=0$ and $Var(\epsilon)=1/2$. However, the shape of $\epsilon$'s distribution varied between the following two possibilities:
\begin{itemize}
\item[Normal] $\epsilon\sim\mathcal{N}(0,1/2)$, as assumed by the mixture model estimator
\item[Uniform] $\epsilon\sim\mathcal{U}(-\sqrt{6}/2,\sqrt{6}/2)$
%\item[Mixture] $f_\epsilon(x)=\frac{1}{4}\phi\left((x+1/3)\sqrt{6}\right)+\frac{1}{4}\phi\left((x-1)\sqrt{6})\right)$
\end{itemize}
%The mixture distribution for $\epsilon$ was designed to be particularly difficult for the mixture model estimator.

When $\beta_1=0$ there is only one mixture component in the control
group, which can be problematic for mixture modeling \citep{griffin2008application,feller2016principal}. Conversely, when $\beta_1=0.3$, unless there is an interaction between $Z$ and covariates (i.e. $\gamma_3\ne 0$), $\eff0=\eff1=0$, so there is no average treatment effect for either principal stratum.

The last two factors---the presence of interactions between covariates and $\st$ and $Z$, respectively---test the performance of a model that does not include interactions when that modeling assumption is false.
When neither interaction was present, $\gamma_2=\gamma_3=0$, then $\gamma_1=1/\sqrt{6}$.
Then, since  $Var(\gamma_1(x_1+x2+x_3))=1/2$ and $Var(\epsilon_i)=1/2$, covariates explained half of the variance of $Y$ within treatment group and principal stratum, and observed covariates $x_1$ and $x_2$ explained 1/3 of that variance.
When there was an interaction between covariates and $\sti$, then $\gamma_1=3/(4\sqrt{6})$ and $\gamma_2=1/(2\sqrt{6})$, so that the slopes for $x_1$ and $x_2$ varied by half their magnitude between principal strata, and on average they were equal to $1/\sqrt{6}$, as in the no-interaction case.
Interactions between covariates and $Z$ were controlled by $\gamma_3$: when there were interactions, $\gamma_3=1/(2sqrt{6})$, otherwise $\gamma_3=0$.

@@

Table \ref{tab:coverate} shows estimates of the empirical coverage of nominal 95\% confidence intervals for GEEPERs and the mixture estimator of $\eff1$, to evaluate their respective standard error estimates and the associated statistical inference.
When $\alpha=0.5$, GEEPERs confidence intervals consistently achieve their nominal levels\footnote{With 500 replications and true coverage probabilities of 0.95, the standard error for empirical coverage rates is approximately 1 percentage point.}, whereas confidence intervals from mixture estimators undercover in the presence of interactions between $Z$ and $X$, or when residuals are non-normal.
When $\alpha=0$ or 0.2, GEEPERs confidence intervals undercover in the presence of interactions between $X$ and $Z$.
Across all conditions in the table, the GEEPERs confidence intervals have higher empirical coverage than their mixture-model counterparts.

@@

\begin{table}
  \input{coverageTab}
  \caption{Emprical coverage of nominal 95\% confidence intervals for GEEPERs and Baysian mixture modeling undery varying conditions.}
  \label{tab:coverage}
\end{table}

@@

We also had access to data on a number of baseline covariates: total scores on a 10-item pretest, fifth-grade stanardized test scores, race/ethnicity (white, Asian, Hispanic/Latino, or Other), indicator variables for if students have an early intervention program (EIP) or individualized educational plan (IEP) in place, if students are learning English as a second language (ESOL), students' average time on task for the pretest (logged), total scores from baseline evaluations of students' math anxiety, negative reaction to math, and numerical confidence, and an indicator for weather students began the school year in remote or in-person instruction.
Students with missing pretest scores were dropped from the analysis; missing data in other covariates was imputed with a Random Forest algorithm \citep{missForest}.
%Table \ref{tab:tab1} describes each covariate--as well as the sucess of the randomForest imputation algorithm.
%% \begin{comment}
%% \begin{table}
%%   \centering
%%   \input{table1}
%%   \caption{Descriptive statistics on baseline covariates, $S$, and $Y$ for the analysis data. Values are mean (SD) unless otherwise noted. Imputation error is the ``out of box'' error estimate from the Random Forest imputation algorithm---root mean squared error divided by the observed standard deviation for continuous variables and misclassification proportion for categorical variables.}
%%   \label{tab:tab1}
%% \end{table}
%% \end{comment}
%% u

@@

We considered several models for the principal score, and full results (which are largely similar to each other) can be found in the online appendix. Here we present results from our model of choice, a logistic regression of observed $S$ on baseline variables chosen with a combination of expert judgement and backwards selection based on the AIC. These included school fixed effects and a set of student-level demographic and educational data: fifth-grade mathematics standardized test scores, %Gender, Race/Ethnicity,
indicator variables for special education status (IEP), whether the student was taking English as a second language (ESOL), whether the student was classified as gifted, and whether students attended a full year of school in 5th grade. Finally, we also included data collected from students at the beginning of the study: the natural logrithm of the  time spent on task during the pretest, scores on baseline measurements of mathematics anxiety and self-efficacy and perceputal sensitivity, along with a missingness indicator for these measurements.
Binned residual plots \citep{gelman2006data} from an initial model fit indicated a curviliniar relationship between perceptual sensitivity measurements (modeled as linear) and model errors, so in the final model we included perceptual sensitivity as a quadratic polynomial.
The model was fit to data from students in the treatment group, for whom bottom-out status ($S$) was observed; hence, the same model fit was used for all three treatment contrasts.

The model was fairly successful in distinguishing bottom-outers from non-bottom-outers---the AUC, evaluated using out-of-sample predictions in a 10-fold cross-validation, was roughly 0.795. That is, in roughly 80\% of bottom-outer/non-bottom-outer pairs of subjects, the bottom-outer will have a higher predicted probability from the model.
Table \ref{tab:results} show the model's coefficient estimates. Noteably, conditional on the other covariates, students with higher fifth-grade standardized test scores were less likely to request many bottom out hints, as were students who spent little time on task during the pretest, while IEP and ESOL students, and students without baseline measurement data, were relatively unlikely to be bottom-outers. The relationship between perceptual sensitivity and bottom out requests was not monotonic---students with average levels were more likely than those with more extreme high or low levels to be bottom-outers; bottom-outers tended to have lower math self-efficacy, but the data are also consistent with a small positive relationship, and there appears to be little to no relationship between math anxiety and bottom-outer status at all.

@@

Figure \ref{fig:effects} plots the estimated principal effects for bottom-outers and non-bottom-outers, using two different models---alongside estimates of the overall average treatment effect, labeled ``ATE.'' In both models, effects were adjusted for all of the variables that were in the principal score model, in addition to students' pretest scores; also, the models substituted class fixed effects for school fixed effects.\footnote{Why use a corser set of fixed effects for the principal score model than the outcome regression? There were two reasons: first, the principal score model was fit to a smaller sample (only students in the ``Instant'' condition), so some classrooms only included one student, which can lead to poor fit. Second, the asymptotics of logistic regression are more restricted than OLS, and so logistic regression tends to perform poorly when the number of parameters increases with the sample size \citep{agresti}.}
The two sets of estimated differed in that the first assumed that coefficients on covariates were equal across principal strata, whereas the second set of results allowed the coefficients on pretest and 5th-grade standardized test scores---the most important predictors of outcomes and principal strata membership, respectively---to vary between strata.

@@

Figure \ref{fig:compare} shows principal effect estimates from GEEPERs (without the $S$-interactions) compared to analogous estimates using Bayesian mixture modeling and PSW.
All three sets of estimates relied on the same principal score model described above, in Section \ref{sec:psMod}, though in the mixture model it was fit simultaneously with effect estimation using a Markov Chain Monte Carlo algorithm \citep{rstan}.
The Bayesian mixture model assumed that outcomes were normally distributed, conditional on covariates (the same as in Section \ref{sec:outMod}) and principal stratum, with a residual standard deviation that varied between principal strata. This modeling assumption is necessarily false, since post-test scores were integers between 0 and 10. All model parameters with support in $\mathbb{R}$ were given standard normal priors, while standard deviation parameters were given half-standard normal priors.
The PSW estimators did not include any covariate outcome modeling. Standard errors for the PSW estimates were estimated using the bootstrap, with resamping done within schools.
For all three sets of estimators, approximate 95\% confidence intervals were estimated by subtracting twice the standard error from the point estimate (or twice the posterior standard deviation from the posterior mean, in the Bayesian mixture model).

@@

\bibliographystyle{unsrtnat}
\bibliography{MOM}
\appendix

@@

\subsection{Proof for Proposition \ref{prop:reg0}}
Carrying out those replacements in \eqref{eq:estEq0}, and rearranging\footnote{Technically, replacing $\tilde{\Psi}_i$ with $\Psi_i=\begin{psmallmatrix} 1 & 0&1&0\\ 0&1&0&1\\0&0&1&0\\0&0&0&1\end{psmallmatrix}\tilde{\Psi}_i$.} gives an equivalent set of estimating equations:
\begin{equation}\label{eq:estEq1}
\sum_{i=1}^{n_C}\Psi_i=\sum_{i=1}^{n_C}\begin{pmatrix}
    Y_i-\muc0-\ri(\muc1-\muc0)-Z_i(\mut0-\muc0)-Z_i\ri(\mut1-\mut0-\muc1+\muc0)\\
    \ri Y_i-\ri\muc0-\ri^2(\muc1-\muc0)-Z_i\ri(\mut0-\muc0)-Z_i\ri^2(\mut0-\mut1-\muc0+\muc1)\\
    Z_iY_i-Z_i\mut0-Z_i\ri (\mut1-\mut0)\\
    Z_i\ri Y_i -Z_i\ri\mut0-Z_i\ri^2(\mut1-\mut0)

>>>>

%%% TO DO
%% Add detail to application section
%% fill in missing citations
%% Appendix
%%   clean up/fix notation for math
%%   add in full simulation results
%%   small interaction simulation
%%   look for what else I promised and either put it in or delete promise
%% proofread

@@

In a separate, if related, line of research, \citet{jo2002}, \citet{ding2011}, \citet{jiangDing2021}, and others have shown that, under certain circumstances, researchers can use baseline covariates to identify and estimate principal effects without relying on principal ignorability.
This paper expands on those identification results by presenting a new set of principal effect estimators, and associated standard error estimates, based on a generalized estimating equations (or M-estimation or method-of-moments) \citep{stefanskiBoos}.
It turns out that, under certain general conditions, principal effects can be estimated with a simple, two-step procedure: first, estimate principal scores with logistic regression or another M-estimator; then, impute unknown principal subgroup membership indicators with principal scores and estimate principal effects using OLS with interactions, just as in the pre-treatment subgroup case.
We will refer to the estimators presented here as ``GEEPERs'': generalized estimating equations for principal effects using regressions.
GEEPERs estimates rely on correct specification of regression functions, but unlike common fully-parametric methods, they make no assumptions about the distribution of regression errors.
Unlike principal score weighting, GEEPERs does not assume principal ignorability, and admits to sandwich-style standard error estimates, which we provide in the appendix.

@@

\subsubsection{Manipulated Factors}
We manipulated six factors in the simulation, listed in Table \ref{tab:factor}.
The six factors are not completely crossed---in particular, we let $n$ and $\alpha$ each vary across all the levels listed while holding the other five factors fixed.

\begin{table}
  \centering
  \begin{tabular}{cc}
    \hline
    Factor &Levels\\
    \hline
Sample size per condition $n$ &$100,200,\dots,1000$\\
$\alpha$ &$0,0.2,0.3,\dots,1$\\
The distribution of $\epsilon_i$& Normal, Uniform\\
$\beta_1$ & 0, 0.3\\
Interactions between $\st$ and covariates & No, Yes\\
Interactions between $Z$ and covariates& No, Yes\\
\hline
  \end{tabular}
  \caption{Manipulated factors in simulation study}
  \label{tab:factor}
  \end{table}

\textbf{\emph{Sample Size per condition $\bm{n}$:}} The guarantees of M-estimation are all asymptotic, so we examined the behavior of our M-estimator at a range of sample sizes to determine its finite-sample properties.

$\bm{\alpha}$\textbf{:} As mentioned above, $\alpha$ controls the variance of the principal scores, i.e. the extent to which $\st$ is predictable as a function of covariates. When $\alpha=0$, the covariates are unrelated to $\st$ and principal scores do not vary between participants, violating \eqref{ass:vps}. We expect that the more predictive the covariates, the better the performance of all three estimators.
To aid in the interpretation of the $\alpha$ parameter, the online appendix plots $\alpha$ against the area under the receiver operating characteristic curve for each fitted model (AUC), a common measure of classification accuracy \citep{bradley1997use}---an AUC of 0.5 implies that the model is no better than random guessing, and AUC of 1 implies perfect prediction. For $0.5\le \alpha \le 1$, the average AUC varies from roughly 0.53 to 0.77; for $\alpha=0.5$, the average AUC was roughly 0.675.

\textbf{\emph{The distribution of $\bm{\epsilon_i}$:}} $\epsilon$ is the regression error in \eqref{eq:y-sim}. Across simulation runs, $E[\epsilon]=0$ and $Var(\epsilon)=1/2$. However, the shape of $\epsilon$'s distribution varied between the following two possibilities:
Normal $\epsilon\sim\mathcal{N}(0,1/2)$, as assumed by the mixture model estimator, or Uniform $\epsilon\sim\mathcal{U}(-\sqrt{6}/2,\sqrt{6}/2)$.
%\item[Mixture] $f_\epsilon(x)=\frac{1}{4}\phi\left((x+1/3)\sqrt{6}\right)+\frac{1}{4}\phi\left((x-1)\sqrt{6})\right)$
%The mixture distribution for $\epsilon$ was designed to be particularly difficult for the mixture model estimator.

$\bm{\beta_1}$\textbf{:} When $\beta_1=0$ there is only one mixture component in the control
group, which can be problematic for mixture modeling \citep{griffin2008application,feller2016principal}. Conversely, when $\beta_1=0.3$, unless there is an interaction between $Z$ and covariates (i.e. $\gamma_3\ne 0$), $\eff0=\eff1=0$, so there is no average treatment effect for either principal stratum.

\textbf{\emph{Interactions between $\st$ or $Z$ and covariates:}} The last two factors---the presence of interactions between covariates and $\st$ and $Z$, respectively---test the performance of a model that does not include interactions when that modeling assumption is false.
When neither interaction was present, $\gamma_2=\gamma_3=0$, then $\gamma_1=1/\sqrt{6}$.
Then, since  $Var(\gamma_1(x_1+x2+x_3))=1/2$ and $Var(\epsilon_i)=1/2$, covariates explained half of the variance of $Y$ within treatment group and principal stratum, and observed covariates $x_1$ and $x_2$ explained 1/3 of that variance.
When there was an interaction between covariates and $\sti$, then $\gamma_1=3/(4\sqrt{6})$ and $\gamma_2=1/(2\sqrt{6})$, so that the slopes for $x_1$ and $x_2$ varied by half their magnitude between principal strata, and on average they were equal to $1/\sqrt{6}$, as in the no-interaction case.
Interactions between covariates and $Z$ were controlled by $\gamma_3$: when there were interactions, $\gamma_3=1/(2sqrt{6})$, otherwise $\gamma_3=0$.

@@

Table \ref{tab:coverage} shows estimates of the empirical coverage of nominal 95\% confidence intervals for GEEPERs and the mixture estimator of $\eff1$, to evaluate their respective standard error estimates and the associated statistical inference.
When $\alpha=0.5$, GEEPERs confidence intervals consistently achieve their nominal levels\footnote{With 500 replications and true coverage probabilities of 0.95, the standard error for empirical coverage rates is approximately 1 percentage point.}, whereas confidence intervals from mixture estimators undercover in the presence of interactions between $Z$ and $X$, or when residuals are non-normal.
When $\alpha=0$ or 0.2, GEEPERs confidence intervals undercover in the presence of interactions between $X$ and $Z$.
Across all conditions in the table, the GEEPERs confidence intervals have higher empirical coverage than their mixture-model counterparts.

@@

\begin{table}
\centering
  \input{coverageTab}
  \caption{Empirical coverage of nominal 95\% confidence intervals for GEEPERs and Bayesian mixture modeling under varying conditions.}
  \label{tab:coverage}
\end{table}

@@

We also had access to data on a number of baseline covariates: total scores on a 10-item pretest, fifth-grade standardized test scores, race/ethnicity (white, Asian, Hispanic/Latino, or Other), indicator variables for if students have an early intervention program (EIP) or individualized educational plan (IEP) in place, if students are learning English as a second language (ESOL), students' average time on task for the pretest (logged), total scores from baseline evaluations of students' math anxiety, negative reaction to math, and numerical confidence, and an indicator for weather students began the school year in remote or in-person instruction.
Students with missing pretest scores were dropped from the analysis; missing data in other covariates was imputed with a Random Forest algorithm \citep{missForest}.
%Table \ref{tab:tab1} describes each covariate--as well as the sucess of the randomForest imputation algorithm.
%% \begin{comment}
%% \begin{table}
%%   \centering
%%   \input{table1}
%%   \caption{Descriptive statistics on baseline covariates, $S$, and $Y$ for the analysis data. Values are mean (SD) unless otherwise noted. Imputation error is the ``out of box'' error estimate from the Random Forest imputation algorithm---root mean squared error divided by the observed standard deviation for continuous variables and misclassification proportion for categorical variables.}
%%   \label{tab:tab1}
%% \end{table}
%% \end{comment}
%% u

@@

We considered several models for the principal score, and full results (which are largely similar to each other) can be found in the online appendix. Here we present results from our model of choice, a logistic regression of observed $S$ on baseline variables chosen with a combination of expert judgement and backwards selection based on the AIC. These included school fixed effects and a set of student-level demographic and educational data: fifth-grade mathematics standardized test scores, %Gender, Race/Ethnicity,
indicator variables for special education status (IEP), whether the student was taking English as a second language (ESOL), whether the student was classified as gifted, and whether students attended a full year of school in 5th grade. Finally, we also included data collected from students at the beginning of the study: the natural logarithm of the  time spent on task during the pretest, scores on baseline measurements of mathematics anxiety and self-efficacy and perceptual sensitivity, along with a missingness indicator for these measurements.
Binned residual plots \citep{gelman2006data} from an initial model fit indicated a curvilinear relationship between perceptual sensitivity measurements (modeled as linear) and model errors, so in the final model we included perceptual sensitivity as a quadratic polynomial.
The model was fit to data from students in the treatment group, for whom bottom-out status ($S$) was observed; hence, the same model fit was used for all three treatment contrasts.

The model was fairly successful in distinguishing bottom-outers from non-bottom-outers---the AUC, evaluated using out-of-sample predictions in a 10-fold cross-validation, was roughly 0.795. That is, in roughly 80\% of bottom-outer/non-bottom-outer pairs of subjects, the bottom-outer will have a higher predicted probability from the model.
Table \ref{tab:results} show the model's coefficient estimates. Notably, conditional on the other covariates, students with higher fifth-grade standardized test scores were less likely to request many bottom out hints, as were students who spent little time on task during the pretest, while IEP and ESOL students, and students without baseline measurement data, were relatively unlikely to be bottom-outers. The relationship between perceptual sensitivity and bottom out requests was not monotonic---students with average levels were more likely than those with more extreme high or low levels to be bottom-outers; bottom-outers tended to have lower math self-efficacy, but the data are also consistent with a small positive relationship, and there appears to be little to no relationship between math anxiety and bottom-outer status at all.

@@

Figure \ref{fig:effects} plots the estimated principal effects for bottom-outers and non-bottom-outers, using two different models---alongside estimates of the overall average treatment effect, labeled ``ATE.'' In both models, effects were adjusted for all of the variables that were in the principal score model, in addition to students' pretest scores; also, the models substituted class fixed effects for school fixed effects.\footnote{Why use a coarser set of fixed effects for the principal score model than the outcome regression? There were two reasons: first, the principal score model was fit to a smaller sample (only students in the ``Instant'' condition), so some classrooms only included one student, which can lead to poor fit. Second, the asymptotics of logistic regression are more restricted than OLS, and so logistic regression tends to perform poorly when the number of parameters increases with the sample size \citep{agresti}.}
The two sets of estimated differed in that the first assumed that coefficients on covariates were equal across principal strata, whereas the second set of results allowed the coefficients on pretest and 5th-grade standardized test scores---the most important predictors of outcomes and principal strata membership, respectively---to vary between strata.

@@

Figure \ref{fig:compare} shows principal effect estimates from GEEPERs (without the $S$-interactions) compared to analogous estimates using Bayesian mixture modeling and PSW.
All three sets of estimates relied on the same principal score model described above, in Section \ref{sec:psMod}, though in the mixture model it was fit simultaneously with effect estimation using a Markov Chain Monte Carlo algorithm \citep{rstan}.
The Bayesian mixture model assumed that outcomes were normally distributed, conditional on covariates (the same as in Section \ref{sec:outMod}) and principal stratum, with a residual standard deviation that varied between principal strata. This modeling assumption is necessarily false, since post-test scores were integers between 0 and 10. All model parameters with support in $\mathbb{R}$ were given standard normal priors, while standard deviation parameters were given half-standard normal priors.
The PSW estimators did not include any covariate outcome modeling. Standard errors for the PSW estimates were estimated using the bootstrap, with resampling done within schools.
For all three sets of estimators, approximate 95\% confidence intervals were estimated by subtracting twice the standard error from the point estimate (or twice the posterior standard deviation from the posterior mean, in the Bayesian mixture model).

@@

\bibliographystyle{plainnat}
\bibliography{MOM}
\appendix

@@

\subsection{Proof for Proposition \ref{prop:reg1}}
Carrying out those replacements in \eqref{eq:estEq0}, and rearranging\footnote{Technically, replacing $\tilde{\Psi}_i$ with $\Psi_i=\begin{psmallmatrix} 1 & 0&1&0\\ 0&1&0&1\\0&0&1&0\\0&0&0&1\end{psmallmatrix}\tilde{\Psi}_i$.} gives an equivalent set of estimating equations:
\begin{equation}\label{eq:estEq1}
\sum_{i=1}^{n_C}\Psi_i=\sum_{i=1}^{n_C}\begin{pmatrix}
    Y_i-\muc0-\ri(\muc1-\muc0)-Z_i(\mut0-\muc0)-Z_i\ri(\mut1-\mut0-\muc1+\muc0)\\
    \ri Y_i-\ri\muc0-\ri^2(\muc1-\muc0)-Z_i\ri(\mut0-\muc0)-Z_i\ri^2(\mut0-\mut1-\muc0+\muc1)\\
    Z_iY_i-Z_i\mut0-Z_i\ri (\mut1-\mut0)\\
    Z_i\ri Y_i -Z_i\ri\mut0-Z_i\ri^2(\mut1-\mut0)
